When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-09-04 doc/paper/abstract.tex
started actual work on revisions, but note for latexdiff to work all edited content must be in same file

The ET response varies due to: 1) climate, with tropical and temperate
climates more likely to exhibit a positive ET response to increasing
VPD than boreal and arctic climates; 2) photosynthesis strategy, with
C3 plants more likely to exhibit a positive ET response than C4
plants; and 3) due to plant type, with crops more likely to exhibit a
positive ET response, and shrubs and gymniosperm trees more likely to
exhibit a negative ET response. These results, derived from previous
literature connecting plant parameters to plant and climate
characteristics, highlight the utility of our simplified framework for
understanding complex land atmosphere systems in terms of idealized
scenarios in which ET responds to VPD only. This response is otherwise
challenging to assess in an environment where many processes co-evolve
together.

>>>>

The ET response varies due to: 1) climate, with tropical and temperate
climates more likely to exhibit a positive ET response to increasing
VPD than boreal and arctic climates; 2) photosynthesis strategy, with
C3 plants more likely to exhibit a positive ET response than C4
plants; and 3) plant type, with crops more likely to exhibit a
positive ET response, and shrubs and gymniosperm trees more likely to
exhibit a negative ET response. These results, derived from previous
literature connecting plant parameters to plant and climate
characteristics, highlight the utility of our simplified framework for
understanding complex land atmosphere systems in terms of idealized
scenarios in which ET responds to VPD only. This response is otherwise
challenging to assess in an environment where many processes co-evolve
together.
